### 2013-09-25 Tex/chapters/conclusion.tex
Korrekturen und Ergänzungen

In this thesis the properties of an Ising ferromagnet, which nodes are
moved by a Gaussian distributed displacement up to the limiting case of
a Poisson process, is studied with Monte Carlo
Simulations. The neighbor relationship is provided by two proximity graphs
-- the RNG and the GG. These graphs conserve the two dimensional character
of the lattice. The coupling constants
are distance dependent, with increasing distance the coupling strength
decreases exponentially.
This model is within the universality of the square lattice Ising
ferromagnet. Its critical temperature decreases with increasing disorder
on a RNG. Since effectively, the decreasing average coordination number
of the underlying graph lowers the resistance to spin flips within
strongly polarized configurations at low temperatures.
 On a GG it first jumps, increases up to a maximum and decreases
afterwards. At high disorder it approaches the limit of randomly generated
graphs of the respective type. The course of the critical temperatures
can be made plausible observing the degree of the underlying graph, an
approximate analytic statement as reason for the observed behavior was
also presented.

>>>>

In this thesis the properties of an Ising ferromagnet, which nodes are
moved by a Gaussian distributed displacement up to the limiting case of
a Poisson process, is studied with Monte Carlo
Simulations. The neighbor relationship is provided by two proximity graphs
-- the RNG and the GG. These graphs conserve the two-dimensional, planar
character of the lattice. The coupling constants
are distance dependent, with increasing distance the coupling strength
decreases exponentially.
This model is within the universality of the square lattice Ising
ferromagnet. Its critical temperature decreases with increasing disorder
on a RNG. The reason is that the decreasing average coordination number
of the underlying graph lowers the resistance to spin flips within
strongly polarized configurations at low temperatures.
On a GG \(T_c\) first jumps, increases up to a maximum and decreases
afterwards. At high disorder it approaches the limit of randomly generated
graphs of the respective type. The course of the critical temperatures
can be made plausible observing the degree of the underlying graph, an
approximate analytic statement as reason for the observed behavior was
also presented.

### 2013-09-25 Tex/chapters/results.tex
Korrekturen und Ergänzungen

    To determine \(T_c\), the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}

@@

@@

    These values of \(T_c\) are plotted over \(\sigma\) in Fig.\ \ref{fig:Tc}.

@@

        In Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
        one can see that these curves are almost identical and the small
        errorbars suggest that they are sufficiently precise for this purpose.

@@

        function, which determines the coupling constants \(J\). As proof for

@@

@@

            \caption[Critical Temperature Normalized by Degree of the Graph]
            {
                Top: Degree \(K\) of graph over different
                disorder parameters \(\sigma\) for
                \subref{sfig:deg:RNG} the RNG and
                \subref{sfig:deg:GG} the GG.
                Bottom: Critical temperatures normalized by degree over different
                disorder parameters for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG.
            }
            \label{fig:Tc_deg}
        \end{figure}\\
        To understand the jump of \(T_c\) it seems to be necessary to
        understand the jump of \(K\), which is easily explained
        by the definition of the GG. As evident from Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
        a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
        To fully understand this, take four nodes forming a square. The edge
        across the diagonal of the plaquette does not exist, because the
        other two nodes are located exactly on the border
        of the lune. Moving one node slightly into the square, causes the lune
        to get smaller, hence no other nodes are inside or on the border of
        the lune anymore and the new diagonal edge appears. This process is sketched in
        Fig.\ \ref{fig:GGEdge}.
        \begin{figure}[htbp]
            \centering
            \subfigure[][]{
                \label{sfig:GGEdge:before}
                \input{images/GGEdgeBefore}
            }
            \subfigure[][]{
                \label{sfig:GGEdge:after}
                \input{images/GGEdgeAfter}
            }
            \caption[Sketch why Many New Edges Arise at the Transition from $\sigma = 0$ to $\sigma > 0$]
            {
                \subref{sfig:GGEdge:before} The edge across does not exist,
                because the other two nodes are on the edge of the lune.
                \subref{sfig:GGEdge:after} Moving one node slightly into the
                square, causes the lune to get smaller, hence no other nodes
                are inside or on the edge of the lune anymore and the edge
                appears.
            }
            \label{fig:GGEdge}
        \end{figure}\\
        Further, the increase of \(T_c\) on the GG can be made plausible.
        Also, the maximum value of \(K\) and the minimum value of \(T_c\)
        are observed at a similar value of \(\sigma\). Hence, while displacing the nodes, there arise more edges
        than edges are vanishing until \(\sigma \approx 0.15\) is reached.
        Then more edges disappear, than appear at further displacement. This
        is not an obvious effect, but can be seen in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}.
        \begin{figure}[htbp]
            \subfigure[][$\sigma = 0.00$]
            {
                \label{sfig:GG_sigma:0.00}
                \includegraphics[width=0.30\textwidth]{images/GG/sigma_e0}
            }
            \subfigure[][$\sigma = 0.01$]
            {
                \label{sfig:GG_sigma:0.01}
                \includegraphics[width=0.30\textwidth]{images/GG/sigma_g0}
            }

@@

    \subsubsection{Influence of the Coupling Constant on the Critical Temperature}%
    \label{sssec:J}
        However, note that the degree does not alone influence the behavior of \(T_c\).
        Further \(T_c\) depends on the coupling constant \(J\), which is
        obvious from Eqs.\ \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
        coupling constant in turn is depending on the length of the edges,
        which changes with \(\sigma\).
        Therefore  in Fig.\ \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
        the mean sum of the coupling constants to all neighbors
        \begin{equation}
            \avg{\sum_{\avg{i,j}} J_{ij}}
        \end{equation}
        is plotted. This is a number which should combine the dependence on
        the degree and the coupling constant. It is determined by summing
        over the edge weights of all edges connected to a node and averaging
        this value over all nodes. Alternatively it is the average edge weight
        of all edges of the graph multiplied by the degree \(\avg{J_{ij}} K\).
        The plots Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
        show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
        \begin{figure}[hbtp]
            \centering
            \subfigure[][]
            {
                \label{sfig:sumJ:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
            }
            \subfigure[][]
            {
                \label{sfig:sumJ:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
            }

@@

            \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
            {
                Top: Mean sum of the coupling constants to all
                neighbors over different disorder parameters for
                \subref{sfig:sumJ:RNG} the RNG and
                \subref{sfig:sumJ:GG} the GG.
                Bottom: Critical temperatures normalized by mean sum of the
                coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
                disorder parameters for
                \subref{sfig:Tc_normJ:RNG} the RNG and
                \subref{sfig:Tc_normJ:GG} the GG.
            }
            \label{fig:TcJ}
        \end{figure}\\
        Though Eq.\ \eqref{eq:exactHCTc} shows that there does not have
        to be a linear connection between \(J\) and \(T_c\), the best guess
        is a linear connection, because this model is derived from the
        square lattice, where the connection is linear. Therefore, one
        normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
        Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
        jump on the GG arises again, but \(T_c\) is now monotonically
        decreasing with increasing disorder parameter \(\sigma\).
        %~ This is a strong hint, that the change of the \(T_c\) with changing
        %~ \(\sigma\) is in some way connected to \(J\) and \(K\) which is an
        %~ expected conclusion.\\
        Moreover the forms of both curves are quite similar, but the
        one for the RNG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
        is generally lower and spans over a bigger temperature range than
        the curve of the GG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
        Both graph types have a plateau at \(0 < \sigma < 0.1\). The conclusion
        is that small disorder has little influence on this normalized critical
        temperature.
        Also both graph types exhibit a steep decline after the plateau before
        they approach an asymptotic limit for \(\sigma \gg 1\).\\
        If one looks at the behavior of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
        for \(\sigma \ll 1\) and consequently \(d_{ij} \approx 1\), the
        following approximation is valid.
        \begin{equation}
            \abs{1-d_{ij}} := \varepsilon \ll 1
        \end{equation}
        \begin{equation}
            J_{ij} = e^{\pm \alpha \varepsilon} \approx 1 \pm \varepsilon \mp \dots
        \end{equation}
        \begin{align}
            \avg{\sum_{\avg{i,j}} J_{ij}} &= \avg{\sum_{\avg{i,j}} (1 \pm \varepsilon)} \\
                                          &= \frac{1 \pm \varepsilon}{N} \sum_{\avg{i,j}} 1 \\
                                          &= K(1 \pm \varepsilon) \approx K
        \end{align}
        Therefore this normalization is independent of the choice of \(\alpha\)
        at small values of \(\sigma\). In Sec.\ \ref{appendix:fixedCoupling}
        in Fig.\ \ref{fig:Tc_deg_A0}\subref{sfig:Tc_norm_deg:RNG_A0}\subref{sfig:Tc_norm_deg:GG_A0}
        the values from Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
        are compared to \(T / K\) for \(\alpha = 0\).

@@

\subsection{Critical Value of the Binder Cumulant}
    The value of the Binder cumulant at the critical point \(g_c\)
    depends strongly on boundary conditions but only weakly on the precise lattice
    structure \cite{BinderValue}. For periodic boundary conditions on a
    square lattice it is \(g_c \approx 0.916\) according to \cite{BinderValue}
        \footnote{Note that \cite{BinderValue} uses another definition of
            the Binder cumulant, and has to be normalized by \(\frac{2}{3}\)
            to match the definition in this thesis.}.
    Because the analysis of Sec.\ \ref{ssec:binderIntersections}
    yields \(g_c\) anyway, it is easy to check the consistency and
    behavior of \(g_c\) in the geometrically disordered Ising model.
    The error bars are the standard error of the six values obtained
    through the intersections.\\
    \begin{figure}[htbp]
        \centering
        \subfigure[for a RNG][]
        {
            \label{sfig:TcG:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_TcG}
        }
        \subfigure[for a GG][]
        {
            \label{sfig:TcG:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_TcG}
        }
        \caption[Values of the Binder Cumulant at the Critical Point $g_c$]
        {
            Values of the Binder cumulant at the critical point \(g_c\)
            for
            \subref{sfig:TcG:RNG} a RNG and
            \subref{sfig:TcG:GG} a GG for different \(\sigma\).
            The dotted line is the reference value for square lattices
            with periodic boundary conditions \cite{BinderValue}, which
            corresponds to \(\sigma = 0\).
        }
        \label{fig:TcG}
    \end{figure}\\
    Considering both plots in Fig.\ \ref{fig:TcG}, \(g_c\) is for low
    \(\sigma\) obviously always bigger than the known value. Though the
    deviations are only very small. Perhaps this overestimation is caused
    by the cubic spline interpolation used to acquire these \(g_c\) values.
    Or this are again finite size effects which would disappear for
    larger system sizes.
    For bigger \(\sigma\) the uncertainty gets greater, but the values
    do only differ by a few percent, hence even the big disorder and
    definition of nearest neighbors via a proximity graph does not change
    the value of \(g_c\) much. Though it is mentioned in \cite{BinderValue} that the
    lattice structure has a minor effect on \(g_c\), the uncertainty of
    \(g_c\) is too large to observe this. For a more exact analysis, new
    Monte Carlo simulations at \(T_c\) would be needed. But this is
    beyond the scope of this thesis. Anyway, the results are the expected
    behavior, because no major deviations from the value of \(g_c\) at
    \(\sigma = 0\) occur at larger \(\sigma\). Within error bars the
    values are all in reasonable agreement with \(g_c\).

>>>>

    To determine \(T_c\), the six unique intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}} \(\in \{(16,32),(16,64),(16,128),(32,64),(32,128),(64,128)\}\)

@@

    \begin{table}[htb]

@@

    These values of \(T_c\) are plotted as a function of \(\sigma\) in Fig.\ \ref{fig:Tc}.

@@

        %~ In Fig.\ \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
        %~ one can see that these curves are almost identical and the small
        %~ errorbars suggest that they are sufficiently precise for this purpose.
        The great influence of \(K\) on \(T_c\) is shown in Fig.\ \ref{fig:Tc_K}.
        But the discontinuity at \(K \approx 4\) and slight curvature at
        \(K \approx 5\) proof that it is not the only influence.
        \begin{figure}[htb]
            \includegraphics[width=0.45\textwidth]{plots/Tc_K}
            \caption[Critical Temperature as a Function of the Degree of the Graph]
                The critical temperature is plotted as a function of the
                degree. There seems to be an in first approximation linear
                dependency. But at \(K \approx 4\) the jump also seen in
                Fig.\ \ref{fig:Tc} occurs. Also slight curvature can be
                recognized and is further examined in Fig.\ \ref{fig:Tc_deg}.
            \label{fig:Tc_K}

@@

        function, which determines the local coupling constants \(J_{ij}\). As proof for

@@

        \begin{figure}[htb]

@@

            \caption[Critical Temperature Normalized by Degree of the Graph]
            {
                Top: Degree \(K\) of graph over different
                disorder parameters \(\sigma\) for
                \subref{sfig:deg:RNG} the RNG and
                \subref{sfig:deg:GG} the GG.
                Bottom: Critical temperatures normalized by degree over different
                disorder parameters for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG.
            }
            \label{fig:Tc_deg}
        \end{figure}\\
        To understand the jump of \(T_c\) it seems to be necessary to
        understand the jump of \(K\), which is easily explained
        by the definition of the GG. As evident from Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
        a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
        To fully understand this, take four nodes forming a square. The edge
        across the diagonal of the plaquette does not exist, because the
        other two nodes are located exactly on the border
        of the lune. Moving one node slightly into the square, causes the lune
        to get smaller, hence no other nodes are inside or on the border of
        the lune anymore and the new diagonal edge appears. This process is sketched in
        Fig.\ \ref{fig:GGEdge}.
        \begin{figure}[htb]
            \centering
            \subfigure[][]{
                \label{sfig:GGEdge:before}
                \input{images/GGEdgeBefore}
            }
            \subfigure[][]{
                \label{sfig:GGEdge:after}
                \input{images/GGEdgeAfter}
            }
            \caption[Sketch why Many New Edges Arise at the Transition from $\sigma = 0$ to $\sigma > 0$]
            {
                \subref{sfig:GGEdge:before} The edge across does not exist,
                because the other two nodes are on the edge of the lune.
                \subref{sfig:GGEdge:after} Moving one node slightly into the
                square, causes the lune to get smaller, hence no other nodes
                are inside or on the edge of the lune anymore and the edge
                appears.
            }
            \label{fig:GGEdge}
        \end{figure}\\
        Further, the increase of \(T_c\) on the GG can be made plausible.
        Also, the maximum value of \(K\) and the maximum value of \(T_c\)
        are observed at a similar value of \(\sigma\). Hence, while displacing the nodes, there arise more edges
        than edges are vanishing until \(\sigma \approx 0.15\) is reached.
        Then more edges disappear than appear at further displacement. This
        is not an obvious effect, but can be seen in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}.
        \begin{figure}[htb]
            \subfigure[][$\sigma = 0.00$]
            {
                \label{sfig:GG_sigma:0.00}
                \includegraphics[width=0.30\textwidth]{images/GG/sigma_e0}
            }
            \subfigure[][$\sigma = 0.01$]
            {
                \label{sfig:GG_sigma:0.01}
                \includegraphics[width=0.30\textwidth]{images/GG/sigma_g0}
            }

@@

    \subsubsection{Influence of the Coupling Constant on the Critical Temperature}%
    \label{sssec:J}
        However, note that the degree does not alone influence the behavior of \(T_c\).
        Further \(T_c\) depends on the coupling constant \(J_{ij}\), which is
        obvious from Eqs.\ \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
        coupling constant in turn is depending on the length of the edges,
        which changes with \(\sigma\).
        Therefore  in Fig.\ \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
        the mean sum of the coupling constants to all neighbors
        \begin{equation}
            \avg{\sum_{\avg{i,j}} J_{ij}}
        \end{equation}
        is plotted. This is a number which should combine the dependence on
        the degree and the coupling constant. It is determined by summing
        over the edge weights of all edges connected to a node and averaging
        this value over all nodes. Alternatively it is the average edge weight
        of all edges of the graph multiplied by the degree \(\avg{J_{ij}} K\).
        The plot Fig.\ \ref{fig:Tc_J} shows that
        there is a less obvious dependency between \(T_c\) and \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
        than between \(T_c\) and \(K\) (c.f.\ Fig.\ \ref{fig:Tc_K}).
        \begin{figure}[htbp]
            \centering
            \includegraphics[width=0.45\textwidth]{plots/Tc_J}
            \caption[Critical Temperature as a Function of the Degree of the Graph]
            {
                The critical temperature is plotted as a function of the
                average edge weight. T
            }
            \label{fig:Tc_J}
        \end{figure}\\
        Though Eq.\ \eqref{eq:exactHCTc} and Fig.\ \ref{fig:Tc_J} show
        that there is no linear connection between \(J\) and \(T_c\), the best guess
        is a linear connection, because this model is derived from the
        square lattice, where the connection is linear. Therefore, one
        normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
        Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
        jump on the GG arises again, but \(T_c\) is now monotonically
        decreasing with increasing disorder parameter \(\sigma\).
        \begin{figure}[hbt]
            \centering
            \subfigure[][]
            {
                \label{sfig:sumJ:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
            }
            \subfigure[][]
            {
                \label{sfig:sumJ:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
            }

@@

            \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
            {
                Top: Mean sum of the coupling constants to all
                neighbors over different disorder parameters for
                \subref{sfig:sumJ:RNG} the RNG and
                \subref{sfig:sumJ:GG} the GG.
                Bottom: Critical temperatures normalized by mean sum of the
                coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
                disorder parameters for
                \subref{sfig:Tc_normJ:RNG} the RNG and
                \subref{sfig:Tc_normJ:GG} the GG.
            }
            \label{fig:TcJ}
        \end{figure}\\
        %~ This is a strong hint, that the change of the \(T_c\) with changing
        %~ \(\sigma\) is in some way connected to \(J\) and \(K\) which is an
        %~ expected conclusion.\\
        Moreover the forms of both curves are quite similar, but the
        one for the RNG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
        is generally lower and spans over a bigger temperature range than
        the curve of the GG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
        Both graph types have a plateau at \(0 < \sigma < 0.1\). The conclusion
        is that small disorder has little influence on this normalized critical
        temperature.
        Also both graph types exhibit a steep decline after the plateau before
        they approach an asymptotic limit for \(\sigma \gg 1\).\\
        If one looks at the behavior of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
        for \(\sigma \ll 1\) and consequently \(d_{ij} \approx 1\), the
        following approximation is valid.
        \begin{equation}
            \abs{1-d_{ij}} := \varepsilon \ll 1
        \end{equation}
        \begin{equation}
            J_{ij} = e^{\pm \alpha \varepsilon} \approx 1 \pm \varepsilon \mp \dots
        \end{equation}
        \begin{align}
            \avg{\sum_{\avg{i,j}} J_{ij}} &\approx \avg{\sum_{\avg{i,j}} (1 \pm \varepsilon)} \\
                                          &= \frac{1 \pm \varepsilon}{N} \sum_{\avg{i,j}} 1 \\
                                          &= K(1 \pm \varepsilon) \approx K
        \end{align}
        Therefore this normalization is independent of the choice of \(\alpha\)
        at small values of \(\sigma\). In Sec.\ \ref{appendix:fixedCoupling}
        in Fig.\ \ref{fig:Tc_deg_A0}\subref{sfig:Tc_norm_deg:RNG_A0}\subref{sfig:Tc_norm_deg:GG_A0}
        the values from Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
        are compared to \(T / K\) for \(\alpha = 0\).

@@

\subsection{Critical Value of the Binder Cumulant}
    The value of the Binder cumulant at the critical point \(g_c\)
    depends strongly on boundary conditions but only weakly on the precise lattice
    structure \cite{BinderValue}. For periodic boundary conditions on a
    square lattice it is \(g_c \approx 0.916\) according to \cite{BinderValue}
        \footnote{Note that \cite{BinderValue} uses another definition of
            the Binder cumulant, and has to be normalized by \(\frac{2}{3}\)
            to match the definition in this thesis.}.
    Because the analysis of Sec.\ \ref{ssec:binderIntersections}
    yields \(g_c\) anyway, it is easy to check the consistency and
    behavior of \(g_c\) in the geometrically disordered Ising model.
    The error bars are the standard error of the six values obtained
    through the intersections.\\
    \begin{figure}[htbp]
        \centering
        \subfigure[for a RNG][]
        {
            \label{sfig:TcG:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_TcG}
        }
        \subfigure[for a GG][]
        {
            \label{sfig:TcG:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_TcG}
        }
        \caption[Values of the Binder Cumulant at the Critical Point $g_c$]
        {
            Values of the Binder cumulant at the critical point \(g_c\)
            for
            \subref{sfig:TcG:RNG} a RNG and
            \subref{sfig:TcG:GG} a GG for different \(\sigma\).
            The dotted line is the reference value for square lattices
            with periodic boundary conditions \cite{BinderValue}, which
            corresponds to \(\sigma = 0\).
        }
        \label{fig:TcG}
    \end{figure}\\
    Considering both plots in Fig.\ \ref{fig:TcG}, \(g_c\) is for low
    \(\sigma\) obviously always bigger than the known value. Though the
    deviations are only very small. Perhaps this overestimation is caused
    by the cubic spline interpolation used to acquire these \(g_c\) values.
    Or this are again finite size effects which would disappear for
    larger system sizes.
    For bigger \(\sigma\) the uncertainty gets greater, but the values
    do only differ by a few percent, hence even the big disorder and
    definition of nearest neighbors via a proximity graph does not change
    the value of \(g_c\) much. Though it is mentioned in \cite{BinderValue} that the
    lattice structure has a minor effect on \(g_c\), the uncertainty of
    \(g_c\) is too large to confirm this. For a more exact analysis, new
    Monte Carlo simulations at \(T_c\) would be needed. But this is
    beyond the scope of this thesis. Anyway, the results show the expected
    behavior, because no major deviations from the value of \(g_c\) at
    \(\sigma = 0\) occur at larger \(\sigma\). Within error bars the
    values are all in reasonable agreement with \(g_c\).
